---
title: "DV_RProject2"
output: html_document
---

Natasha Halfin, Evan Johnston, Kaylyn Zvonek

For this project, we used a dataset containing information on the top 5000 companies in the country, including their state, city, industry, revenue, and percentage of growth.

```{r, echo = FALSE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
library("plyr")
library("RCurl")
library("reshape2")
library("tidyr")
library("dplyr")


```

```{r, eval = TRUE, echo = FALSE}
source("../01 Data/data.R")
source("../02 Data Wrangling/dataWrangling.R")
```

This is a dataframe of our entire dataset.

```{r, eval =TRUE, echo=FALSE}
data.frame(head(companyData))
```


This is a dataframe of wrangled data that indicates the average revenue and growth across each industry.
```{r, eval =TRUE, echo=FALSE}
data.frame(head(industryGrowthData))
```

This is a wrangled dataframe displaying companies in Texas and California
```{r, eval =TRUE, echo=FALSE}
data.frame(head(txCaCompanyData))
```

This wrangled dataframe shows the highest revenue and growth by state.
```{r, eval =TRUE, echo=FALSE}
data.frame(head(stateGrowth))
```
This wrangled dataframe indicates the lowest revenue and growth by city.
```{r, eval =TRUE, echo=FALSE}
data.frame(head(cityGrowth))
```
Data Visualizations (EVAN NEED 4 HERE based on wrangled dataframes above)


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
